### 2022-01-24 input/experiments.tex
meow

This section aims to answer the following questions about \NAME: What
is the overhead of reaching consistent partitioning using \NAME in
large scale networks?  Is \NAME relevant in Edge infrastructures where
\processes are geo-distributed into clusters? We performed the
experimentation using PeerSim, a simulator written in Java that allows
researchers to evaluate and assess distributed algorithms in large
scale networks~\cite{montresor2009peersim}. The code is available on
the Github platform at
\TODO{\url{https://anonymous.4open.science/r/peersim-partition-5592}}.

@@

\noindent Figure~\ref{fig:geant} confirms that concurrent
\texttt{Add}s may reach consistent partitioning faster. In particular,
the top part of Figure~\ref{fig:geant} depicts a slow down in traffic
around $500$ ms due to the high latency inter-continental link. The
first plateau shows the source's autonomous system acknowledging this
source, while the second shows the other autonomous system catching
up.  The inter-continental link is a bottleneck that does not exist
when each cluster has its own source.

\noindent Figure~\ref{fig:geant} highlights that removing the
inter-continental link generates additional traffic. The cluster cut
off from the source must purge all control information about this
source.  Most importantly, Figure~\ref{fig:geant} shows that \NAME
still operates well when \emph{physical} partitions appear. \Processes
from the cluster without source do not belong to any partition while
\processes from the other cluster belong to the same partition.

@@

\begin{asparadesc}
  \item[Objective:] Highlight the shortcoming of \NAME in Edge
    infrastructures and propose an improvement called \NAMEC (stands
    for \underline{cross} \underline{\NAME}) that fits this context by
    enabling lazy dynamic partitioning.

@@

    \noindent We evaluate \NAME against an extension of \NAME called
    \NAMEC that enables lazy dynamic partitioning by allowing gateways
    to stop notifications when their respective network does not
    appear to have a source. Using \NAMEC, each \process maintains a
    \emph{local} index that corresponds to the best partition of its
    autonomous systems, and a \emph{global} index that corresponds to
    the best partition cross autonomous systems, \ie adjacent
    autonomous systems that have at least one source.

>>>>

This section aims to answer the following questions about \NAME: What
is the overhead of reaching consistent partitioning using \NAME in
large scale networks?  Is \NAME relevant in Edge infrastructures where
\processes are geo-distributed into clusters? We performed the
experimentation using PeerSim, a simulator written in Java that allows
researchers to evaluate and assess distributed algorithms in large
scale networks~\cite{montresor2009peersim}. All the code is available
on the Github platform at
\TODO{\url{https://anonymous.4open.science/r/peersim-partition-5592}}.

@@

\noindent Figure~\ref{fig:geant} confirms that concurrent
\texttt{Add}s may reach consistent partitioning faster. In particular,
the top part of Figure~\ref{fig:geant} depicts a slow down in traffic
around $300$ ms due to the high latency inter-continental link. The
first plateau shows the source's autonomous system acknowledging this
source, while the second shows the other autonomous system catching
up.  The inter-continental link is a bottleneck that does not exist
when each cluster has its own source.

\noindent Figure~\ref{fig:geant} highlights that \NAME operates well
even when \emph{physical} partitions appear. Indeed, the disconnection
of the only inter-continental link existing between the two clusters
either leads to 
\begin{inparaenum}[(i)]
\item additional traffic when the \processes do not have any source in
  their cluster, for \processes need to purge all indexes about the
  remote unreachable source until reaching consistent partitioning; or
\item an already consistent partitioning, for \processes of each
  cluster already target the source in their respective cluster.
\end{inparaenum}

@@

\begin{asparadesc}
  \item[Objective:] Highlight the shortcoming of \NAME in Edge
    infrastructures and propose an improvement called \NAMEC (stands
    for \underline{cross} \underline{\NAME}) that enables \emph{lazy}
    dynamic partitioning by allowing gateways to stop notifications
    when their respective network does not appear to have a source.

@@

    \noindent We evaluate \NAME against \NAMEC. Using \NAMEC, each
    \process maintains a \emph{local} index that corresponds to the
    best partition of its autonomous systems, and a \emph{global}
    index that corresponds to the best partition cross autonomous
    systems, \ie adjacent autonomous systems that have at least one
    source.
